Outline

### 2024-04-10 04-Various/Outline.qmd
Update some docs
Update outline

---
format: html
---

@@

1. Please feel free to add topics to the outline. This is just based on some brief brain storming and more a conversation starter
2. Please feel free to add your name to a section as lead. Of course multiple people can work on one section
3. Please feel free to add general comments, remarks, etc.

@@

- Introduction to landscape ecology (*Hesselbarth*)
  - Definition of landscape ecology
  - Brief history of landscape ecology
  - Computational aspects of landscape ecology
- Open source vs. proprietary software
- GUI vs. script based software
- Programming language
  - R (*Hesselbarth*, *Nowosad*)
  - Python (*Bosch*)
  - Julia (*Schouten*)
- Classic/traditional tools
- Upcoming/modern tools
  - AI/ML tools
  - Virtual reality
- Spatial planning perspective (*Jung*)
- Spatial patterns (*Nowosad*, *Hesselbarth?*)
- Landscape genetics (*Breitbart*)

@@

-	Remote sensing?
-	General spatial data developments?

# Literature to look at
[10.1007/s10980-021-01366-9](www.doi.org/10.1007/s10980-021-01366-9)

>>>>

---
title: Outline
format: html
---

@@

1. Please feel free to add topics to the outline. This is just based on some brief brain storming and more a conversation starter
2. Please feel free to add your name to a section as lead. Of course multiple people can work on one section
3. Please feel free to add general comments, remarks, etc. (using your initals)
4. Knit and push changes

@@

- Introduction to landscape ecology (*Hesselbarth*)
  - Brief definition of landscape ecology
  - Computational aspects of landscape ecology
- Software and programming language for landscape ecology
  - Open source vs. proprietary software
  - GUI vs. script based software
  - Programming language
    - R (*Hesselbarth*, *Nowosad*)
    - Python (*Bosch*)
    - Julia (*Schouten*)
- Computational methods
  - Visualization (i.e., maps)
  - Spatial patterns (*Nowosad*, *Hesselbarth?*)
  - Connectivity
  - Simulations (e.g., neutral landscapes) (*Hesselbarth*)
  - Optimization
  - Spatial planning perspective (*Jung*)
  - Landscape genetics (*Breitbart?*)
- Discussion
  - General spatial data developments
  - AI impacts on landscape ecology

@@

-	Remote sensing developments?
